One exact and one random sampling method to assess the reliability of inferences from network enrichment analysis

### 2018-05-08 doc/genesetdp.tex
Added discussion on depletion.

>>>>

Both our implementations, GeneSetDP and GeneSetMC, are intended for measuring enrichment of links between the query and the pathway set of genes. Most other NEA methods also report depletion of such links. One could easily modify our code to instead of only measuring the higher scoring tail measuring both tails of $N(s)$. However, this might result in a drop in sensitivity, so we have so far no implemented such a mechanism.
